\begin{result}{12.399020835139504}{Pan, Richard (Legislator) Assembly}
\textbf{This is the proof of why SB 277 is needed to protect the public from vaccine preventable contagions. SB 277 is also needed to protect our most vulnerable citizens. Vaccine preventable infections are particularly dangerous to people with cancer, transplants, and other immune disorders.
}\end{result}

\begin{result}{11.715124538755342}{Loe Fisher, Barbara (GeneralPublic) Assembly}
\textbf{It fails to value the health and educational needs of vulnerable children, for whom the risk of vaccination have been or will turn out to be 100\%. No doctor in California or public health official at the CDC in Atlanta can accurately predict whether or not a child will suffer brain inflammation, injury or death after vaccination.
}\end{result}

\begin{result}{10.650676879567987}{Blumberg, Dean (GeneralPublic) Assembly}
\textbf{And thank goodness that there were no deaths due to measles, but make no mistake, measles can be deadly, with one death out of every thousand cases. In fact, more children have died from measles than any other disease. That's why SB 277 is needed.
}\end{result}

\begin{result}{10.277112279676443}{Henry, Hannah (GeneralPublic) Assembly}
\textbf{The personal belief exemption is an artifact of a time when we collectively understood the need and value of vaccination. But as more and more parents have chosen their own schedule, their own version of the truth about vaccines, and as those people have clustered in like-minded circles, dangerous pockets of vulnerability have developed.
}\end{result}

\begin{result}{9.180445533243097}{Pan, Richard (Legislator) Assembly}
\textbf{Both protection of the public and children from death and disability due to preventable communicable diseases, and ensuring children with special needs their right to an education, are compelling interests to require all students be vaccinated unless granted a medical exemption.
}\end{result}

\begin{result}{9.135690999540271}{Pan, Richard (Legislator) Senate}
\textbf{That is proof of why SB 277 is necessary to protect the public from vaccine preventable contagions. In addition, vaccine preventable infections are particularly dangerous to children who have cancer, may have transplants, or immune diseases. These children are particularly vulnerable to infection and they depend on community immunity to prevent the contagion from actually reaching them.
}\end{result}

\begin{result}{8.830523154233383}{Pan, Richard (Legislator) Senate}
\textbf{Both protection of the public and children from death and disability due to preventable communicable diseases and assuring that children with special needs, their right to an education, are compelling interests to require all students be vaccinated unless they are granted a medical exemption. Thank you.
}\end{result}

\begin{result}{8.67213374776659}{Jensen, Jena (GeneralPublic) Senate}
\textbf{So I wanted to let you know, for those of you who don't already know, being located in Orange County near Disneyland, we did have eight cases of Measles come into our emergency department, children with Measles come into our ED this winter. Five out of the eight were so sick that they needed to be hospitalized.
}\end{result}

\begin{result}{8.587621734089648}{Huff, Bob (Legislator) Senate}
\textbf{It certainly has saved us from a lot of childhood deaths and other things. But not everything in life is easily accomplished with advancements without trade-offs on the other side. And so, where I am leaning right now and I'll probably vote is against your bill, because I think the trade-off of giving up personal freedoms, even if your child gets sick because of that personal freedom or personal choice, I think that that's a threshold that should be very carefully evaluated before we hand it over to a government mandate.
}\end{result}

\begin{result}{8.02002802077853}{Pan, Richard (Legislator) Assembly}
Keep them free from disease. That's freedom. Not to be sick. And we need to be sure that that is what we strive for. I respectfully ask for an aye vote. And thanks again. I want to thank the committee and members for your thoughtful discussion.
\end{result}

