\begin{result}{20.040584586913265}{Huff, Bob (Legislator) Senate}
\textbf{We don't say, "Have you got your 27 vaccines," or whatever it is, before they come and go to Disneyland, or any other place. And so, you're requiring our own parents to jump through hoops to do all these things in the interest of public health; and yet, we're still exposed.
}\end{result}

\begin{result}{15.249840257951574}{Huff, Bob (Legislator) Senate}
\textbf{If I was a parent and I had a child in that category, from what I'm hearing, I wouldn't trust the public school anyway, and yet it seems like you'd want to create a safe cocoon around them as much as you can; and yet, we're jumping through a lot of hoops to force a lot of other people out when we still don't have a safe situation in school.
}\end{result}

\begin{result}{7.7821422973482175}{Bonta, Rob (LegStaff) Assembly}
Wait a second, wait a second, let me jump in here
\end{result}

\begin{result}{7.7821422973482175}{Bonta, Rob (Legislator) Assembly}
Wait a second, wait a second, let me jump in here
\end{result}

\begin{result}{7.660613415956397}{Bonta, Rob (LegStaff) Assembly}
All right. Let me just jump in here. We talked about narrow tailoring earlier, and I want to ask you to narrowly tailor your responses to the questions of the members. Answer their question. And then stop and see if they have another question. And we'll move through the member questions and get on to public comment. Dr. Wood, do you have any more questions?
\end{result}

\begin{result}{7.660613415956397}{Bonta, Rob (Legislator) Assembly}
All right. Let me just jump in here. We talked about narrow tailoring earlier, and I want to ask you to narrowly tailor your responses to the questions of the members. Answer their question. And then stop and see if they have another question. And we'll move through the member questions and get on to public comment. Dr. Wood, do you have any more questions?
\end{result}

\begin{result}{7.032216048716612}{Reiss, Dorit (GeneralPublic) Senate}
We don't change the curriculum to prevent parents from having to choose between a curriculum they don't like and homeschooling. It's problematic to say we need to do away with a reasonable health and safety requirement, vaccination to prevent parents from having to choose between following the requirement and choosing another educational option, again, home schooling or independent study.
\end{result}

\begin{result}{6.846770329405164}{Reiss, Dorit (GeneralPublic) Senate}
The second point is the courts don't require a religious exemption. Again emphasized that parental rights and religious rights don't allow the parents to expose the community to ill health and to disease and every court since have followed that precedent.
\end{result}

\begin{result}{6.547916404088606}{Anderson, Joel (Legislator) Senate}
And when you're facing a parent who has gone through that turmoil and they say gosh, we don't agree with you. At that point, do you continue on and say I know better and I don't care what risk it is to your family? We have some folks who said they had two children who went through it. So, how many children do you have to punish my family before enough is enough?
\end{result}

\begin{result}{6.444506986525054}{Huff, Bob (Legislator) Senate}
We have other immunizations that we require that don't have as much reliability as we'd like, so they're able to spread their disease. And yet, we're trying to keep a safe place at school for those that are compromised, their immune system is compromised through chemotherapy or lupus or whatever it is.
\end{result}

